---
title: "RMarkdown Test Document"
author:
- Author 1
- Author 2
date: Last compiled on `r format(Sys.time(), '%B %d, %Y')` at `r format(Sys.time(),'%l:%M %p - %Z')`
output:
  html_document: 
    toc: true
    number_sections: true
    toc_float: true
  word_document:
    toc: true
    number_sections: true
  pdf_document: 
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message = FALSE)
```

# First Header

Insert inline LaTex between dollar signs, e.g. $\mu$. A great online equation editor for LaTex may be found at CodeCogs (<https://latex.codecogs.com/eqneditor/editor.php>)

## First Subheader

Can insert LaTex on its own line between double dollar signs, e.g.

$$
x+\frac{1}{2}=\gamma_1
$$

Text between double stars is **bold**. Bulleted Lists have a - in front

-   List item 1

-   List item 2

# Second Header

Add a new R code chunk by clicking the *Insert Chunk* button on the toolbar

```{r}
head(cars)
```

If knitting to html, dataframes with many columns may be paged with rmarkdown:paged_table. Will not work with Word or PDF

```{r}
#rmarkdown::paged_table(head(cars))
```

Dataframes in Word and PDF (as well at html) may be alternatively formatted with knitr::kable.

```{r}
knitr::kable(head(cars))
```

Output may be displayed without code using echo=FALSE. This is not recommended unless you show the complete code at the end of the document.

```{r echo=FALSE}
mean(cars$speed)
```

Graphics/Plots may be displayed as well

```{r}
plot(cars)
```

# Complete R Code

It is a good idea to include this at the end of every RMarkdown document

```{r eval=FALSE}
head(cars)
knitr::kable(head(cars))
mean(cars$speed)
plot(cars)
```
